Methodology for Assessing the State of the Practice for Domain X

### 2020-10-29 StateOfPractice/Methodology/Methodology.tex
added comments from meeting regarding Rank Short List section of Methodology

\section{Rank Short List} \label{SecRankShortList}
An AHP pairwise comparison between the short list packages with respect to usability and modifiability survey results, as well as performance benchmarks, is conducted by the domain expert. The tool can be found here. The usability and modifiability survey can be found \href{https://github.com/smiths/AIMSS/blob/master/StateOfPractice/Methodology/Experiments.pdf}{here}. Performance benchmarks can be found here.
\pmi{are we adding a tool for this?}
\pmi{performance benchmarks will be domain specific, how to proceed with providing a resource/guidance?}

>>>>

\section{Rank Short List} \label{SecRankShortList}

\pmi{comments from meeting: this part is to `enable conversation'; the ranking starts the conversation - `why do they like this software'; yes to tool question - spreadsheet; enable conversation regarding what's good about the specific softwares (also important highlights of domain software?); drop performance benchmarks}

An AHP pairwise comparison between the short list packages with respect to usability and modifiability survey results, as well as performance benchmarks, is conducted by the domain expert. The tool can be found here. The usability and modifiability survey can be found \href{https://github.com/smiths/AIMSS/blob/master/StateOfPractice/Methodology/Experiments.pdf}{here}. Performance benchmarks can be found here.
\pmi{are we adding a tool for this?}
\pmi{performance benchmarks will be domain specific, how to proceed with providing a resource/guidance?}
